Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-02 supp.rnw
Fix erroneous captions in the supplementary.
Add axis labels to the supplementary partial residual plots.

%TODO: x and y axis labels.
<<echo=FALSE>>=
	model_fit_plot <- function(parameters) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)
		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
		return(plot)
	}

@@

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::facet_grid(row_index~col_index)
		return(plot)
	}

@@

	\caption{%
		Plot of model fit using the most parsimonious model.
	}
	\label{fig:model-fit-best}
\end{figure}

@@

	\caption{%
		Partial residuals plot using the most parsimonious model.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}
	\label{fig:partial-residual-best}
\end{figure}

>>>>

<<echo=FALSE>>=
	model_fit_plot <- function(parameters) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)
		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
		return(plot)
	}

@@

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::facet_grid(row_index~col_index) +
			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)")
		return(plot)
	}

@@

	\caption{%
		Plot of model fit using the most parsimonious model.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}
	\label{fig:model-fit-best}
\end{figure}

@@

	\caption{%
		Partial residuals plot using the most parsimonious model.
	}
	\label{fig:partial-residual-best}
\end{figure}
